\chapter{Problem \& Reflections}

The most useful reflection from this project is that many late-stage problems were not purely visual and not purely technical. In practice, presentation, interaction, testing, and process evidence were coupled. Once the team moved beyond the prototype stage, every UI or flow improvement exposed another layer of engineering work: raycast boundaries, runtime layout assumptions, battle-state messaging, or proof that a fix had actually held. This chapter summarises those issues and the team's response in concrete terms \cite{cw1Specification,postWr3IssueLog}.

\section{Technical Problem}

One recurring technical problem was that visual polish changed interaction behaviour. As the title overlay, themed HUD, and hand dock became more elaborate, previously hidden assumptions in the prototype started to fail. Concrete examples included title overlay content colliding vertically, the top-left prompt stack overlapping turn and energy labels, the hand dock obscuring lower units, and action availability being visible only in the battle log. Earlier in the post-WR3 cycle, selection blocking and battle-flow regressions also appeared because UI elements and game-state transitions were still too tightly coupled \cite{postWr3IssueLog}.

The important lesson was that these defects could not be handled with visual tweaking alone. Several bugs existed at the boundary between layout and logic. A panel could look harmless but still intercept clicks; a debug shortcut could speed up testing but bypass the same flow path used by the real HUD; a screenshot could show the board correctly while missing overlay elements entirely. The team therefore adopted a repeatable closure pattern: reproduce the problem in smoke, move any deterministic part of the failure into an EditMode or PlayMode regression test, fix the runtime code, and then rerun smoke for the final visual confirmation. This pattern is one of the strongest practical outcomes of the project because it turned late-stage polish from a subjective exercise into a controlled engineering loop.

Another technical limitation came from tooling. Unity MCP accelerated many inspections and runtime checks, but overlay screenshots were not consistently trustworthy for `Screen Space Overlay` verification in this project setup. Instead of pretending the tooling was sufficient on its own, the team explicitly split responsibility: hierarchy assertions and runtime tests for structural proof, and manual smoke for final overlay readability. That boundary is now documented rather than hidden, which makes the final validation claims more credible \cite{postWr3IssueLog}.

\section{Project Management}

From a project-management perspective, the main challenge was resisting attractive but expensive scope growth. The game concept could easily have drifted toward a larger tactics RPG with more cards, more maps, more animations, and progression systems. Instead, the team kept returning to the vertical-slice rule established earlier in the coursework: build one encounter well, then extend only when the current layer is stable. This is why post-WR3 work was broken into explicit slices such as front-end flow, HUD refactor, gameplay expansion, visual theming, ambience, and feedback completion, rather than into one vague ``polish'' phase.

Testing and evidence collection also became planning tools rather than just report-writing tasks. When a feature area lacked a clear validation path, that was treated as a planning warning sign. For example, purely cosmetic ideas that could not be stabilised or evidenced were deprioritised, while improvements such as disabled-card overlays, world-space health bars, and menu-flow fixes were promoted because they closed visible usability gaps and could be backed by tests or smoke evidence. This made the late project more disciplined: the team was not simply asking what looked better, but what improved the submission package in a demonstrable way.

\section{Team Management}

The team-management story is more mixed, and it is important to describe it honestly. Early collaboration relied heavily on cloud-file passing and chat-based coordination, which was fast but weak for traceability. Later, the team consolidated onto a canonical repository structure with clearer ownership and branch sequencing. That move improved accountability and made the final codebase and document trail much easier to audit, but it also meant that some historical process evidence had to be reconstructed or explicitly marked as incomplete \cite{collaborationHistory,canonicalRepoEvidence}.

This is why several final-report support notes are phrased as claim boundaries rather than polished success stories. The repository now proves a much stronger late-stage workflow than the team had early on, but it does not magically recreate every historical task-board capture or meeting trace. Instead of inventing evidence, the team kept a transparent distinction between what is directly provable from the canonical repository, what has been retrospectively reconstructed, and what remains weaker than ideal. That choice may be less flattering than writing a smooth retrospective, but it is better software-engineering practice and more defensible in assessment terms \cite{taskBoardEvidence}.

The positive lesson is that convergence on one repository and one evidence tree materially improved collaboration. Once responsibilities, milestone notes, issue logs, and report materials lived in the same workspace, ambiguity reduced sharply. In practical terms, the final package is stronger because the team eventually standardised its collaboration process, even if that standardisation came later than it ideally should have.
