\chapter{Test Plan}

The test plan was built backward from the codebase rather than from generic test-type labels. In the final 2026-04-17 report state, the plan is no longer prospective: every scoped runtime class has a direct suite, the smoke path has been rerun, and the supporting records now describe a closed validation cycle rather than a future rerun intention.

\section{Requirements Coverage Matrix}

\setlength{\tabcolsep}{3pt}
\footnotesize
\begin{longtable}{lll}
\caption{Requirements coverage matrix for the final single-battle validation set.}
\label{tab:requirements-coverage}\\
\toprule
\wcell{1.00cm}{\textbf{Req. ID}} & \wcell{3.15cm}{\textbf{Requirement / expected behaviour}} & \wcell{8.35cm}{\textbf{Coverage evidence and validation note}} \\
\midrule
\endfirsthead
\toprule
\wcell{1.00cm}{\textbf{Req. ID}} & \wcell{3.15cm}{\textbf{Requirement / expected behaviour}} & \wcell{8.35cm}{\textbf{Coverage evidence and validation note}} \\
\midrule
\endhead
\wcell{1.00cm}{R-01} & \wcell{3.15cm}{The battle scene must initialise a single playable tactical battle.} & \wcell{8.35cm}{Primary suites: \code{GameRootTests} and \code{BattleFlowPlayModeTests}. Status: Verified. Confirmed by direct bootstrap tests and the PlayMode smoke rerun.} \\
\wcell{1.00cm}{R-02} & \wcell{3.15cm}{Units must register to the correct team and occupy valid starting tiles.} & \wcell{8.35cm}{Primary suites: \code{GameRootTests} and \code{GridManagerTests}. Status: Verified. Registration, placement, and occupancy checks all passed in the consolidated rerun.} \\
\wcell{1.00cm}{R-03} & \wcell{3.15cm}{The player turn must reset card plays and draw a fresh hand each round.} & \wcell{8.35cm}{Primary suites: \code{TurnManagerTests} and \code{DeckManagerTests}. Status: Verified. Turn flow and deck-hand lifecycle are both backed by named reruns.} \\
\wcell{1.00cm}{R-04} & \wcell{3.15cm}{Move cards must allow valid tile movement only.} & \wcell{8.35cm}{Primary suites: \code{CardResolverTests} and \code{GridManagerTests}. Status: Verified. Movement range, placement, and execution branches all passed.} \\
\wcell{1.00cm}{R-05} & \wcell{3.15cm}{Strike cards must damage adjacent enemies and reject friendly targets.} & \wcell{8.35cm}{Primary suites: \code{CardResolverTests} and \code{BattleUITests}. Status: Verified. Direct resolver and UI-triggered strike behaviour are both rerun-backed.} \\
\wcell{1.00cm}{R-06} & \wcell{3.15cm}{Guard cards must apply a temporary defensive state.} & \wcell{8.35cm}{Primary suites: \code{CardResolverTests}, \code{UnitControllerTests}, and \code{BattleUITests}. Status: Verified. Guard resolution, guard consumption, and UI guard flow all passed.} \\
\wcell{1.00cm}{R-07} & \wcell{3.15cm}{Push cards must damage the target and attempt knock-back.} & \wcell{8.35cm}{Primary suites: \code{CardResolverTests} and \code{GridManagerTests}. Status: Verified. Damage plus movement constraints are covered by passing rerun evidence.} \\
\wcell{1.00cm}{R-08} & \wcell{3.15cm}{Enemy turns must target the nearest alive player and either move or attack.} & \wcell{8.35cm}{Primary suites: \code{EnemyAITests} and \code{TurnManagerTests}. Status: Verified. AI selection logic and turn-loop orchestration both have passing rerun evidence.} \\
\wcell{1.00cm}{R-09} & \wcell{3.15cm}{Battle end must lock the loop and expose a consistent outcome state.} & \wcell{8.35cm}{Primary suites: \code{TurnManagerTests} and \code{BattleUITests}. Status: Verified. Earlier regression evidence was preserved and the broader rerun passed.} \\
\wcell{1.00cm}{R-10} & \wcell{3.15cm}{The UI must prompt the player when selection or target conditions are invalid.} & \wcell{8.35cm}{Primary suites: \code{BattleUITests} and \code{CardButtonViewTests}. Status: Verified. Direct UI prompt and button-binding suites both passed in the consolidated rerun.} \\
\bottomrule
\end{longtable}
\normalsize
\setlength{\tabcolsep}{6pt}

\section{Module and Class Coverage Summary}

\setlength{\tabcolsep}{4pt}
\footnotesize
\begin{longtable}{ll}
\caption{Module/class coverage summary for the final validation set.}
\label{tab:module-coverage}\\
\toprule
\wcell{4.55cm}{\textbf{Runtime target and direct evidence}} & \wcell{7.65cm}{\textbf{Covered behaviours and validation status}} \\
\midrule
\endfirsthead
\toprule
\wcell{4.55cm}{\textbf{Runtime target and direct evidence}} & \wcell{7.65cm}{\textbf{Covered behaviours and validation status}} \\
\midrule
\endhead
\wcell{4.55cm}{\code{TurnManager}\\\code{TurnManagerTests}\\3 tests} & \wcell{7.65cm}{Battle start without valid sides, card-play quota consumption, end-turn transition, and battle-end lock. Status: Verified.} \\
\wcell{4.55cm}{\code{DeckManager}\\\code{DeckManagerTests}\\6 tests} & \wcell{7.65cm}{Fallback deck build, draw count, discard handling, reshuffle behaviour, and the empty-deck branch. Status: Verified.} \\
\wcell{4.55cm}{\code{CardResolver}\\\code{CardResolverTests}\\6 tests} & \wcell{7.65cm}{Valid target ranges plus move, strike, guard, push, and invalid/friendly target rejection. Status: Verified.} \\
\wcell{4.55cm}{\code{GridManager}\\\code{GridManagerTests}\\7 tests} & \wcell{7.65cm}{Grid generation, bounds, placement, movement, push limits, neighbour lookup, BFS range, and highlight reset. Status: Verified.} \\
\wcell{4.55cm}{\code{EnemyAI}\\\code{EnemyAITests}\\4 tests} & \wcell{7.65cm}{Manhattan distance, nearest-target selection, step-direction priority, and dead-target skipping. Status: Verified.} \\
\wcell{4.55cm}{\code{UnitController}\\\code{UnitControllerTests}\\6 tests} & \wcell{7.65cm}{HP init, damage, guard reduction, healing clamp, death deactivate, and position sync. Status: Verified.} \\
\wcell{4.55cm}{\code{BattleUI}\\\code{BattleUITests}\\19 tests} & \wcell{7.65cm}{Card selection prompts, strengthened next-step messaging, enemy/action summaries, guard auto-resolve, invalid target rejection, action-log updates, and battle-end UI lock. Status: Verified.} \\
\wcell{4.55cm}{\code{GameRoot}\\\code{GameRootTests}\\2 tests} & \wcell{7.65cm}{Dependency wiring, scene bootstrap, unit registration, and initial battle start. Status: Verified.} \\
\wcell{4.55cm}{\code{TileView}\\\code{TileViewTests}\\3 tests} & \wcell{7.65cm}{Coordinate init, occupancy changes, and visual highlight method safety. Status: Verified.} \\
\wcell{4.55cm}{\code{CardButtonView}\\\code{CardButtonViewTests}\\1 test} & \wcell{7.65cm}{UI button-to-card selection binding. Status: Verified.} \\
\wcell{4.55cm}{Smoke path\\\code{BattleFlow}\\\code{PlayModeTests}\\1 test} & \wcell{7.65cm}{Whole battle bootstrap and first playable state. Status: Verified.} \\
\bottomrule
\end{longtable}
\normalsize
\setlength{\tabcolsep}{6pt}

\section{Representative Test Input and Output Matrix}

\setlength{\tabcolsep}{3pt}
\footnotesize
\begin{longtable}{llllll}
\caption{Representative test-case matrix with explicit inputs and expected outputs.}
\label{tab:test-io-matrix}\\
\toprule
\wcell{0.95cm}{\textbf{ID}} & \wcell{2.20cm}{\textbf{Action / scenario}} & \wcell{2.55cm}{\textbf{Inputs / setup}} & \wcell{2.55cm}{\textbf{Expected output}} & \wcell{2.55cm}{\textbf{Actual output}} & \wcell{2.10cm}{\textbf{Evidence}} \\
\midrule
\endfirsthead
\toprule
\wcell{0.95cm}{\textbf{ID}} & \wcell{2.20cm}{\textbf{Action / scenario}} & \wcell{2.55cm}{\textbf{Inputs / setup}} & \wcell{2.55cm}{\textbf{Expected output}} & \wcell{2.55cm}{\textbf{Actual output}} & \wcell{2.10cm}{\textbf{Evidence}} \\
\midrule
\endhead
\wcell{0.95cm}{TC-01} & \wcell{2.20cm}{Battle bootstrap and first playable state} & \wcell{2.55cm}{Load the battle scene with valid player and enemy rosters.} & \wcell{2.55cm}{Scene initialises, units spawn onto legal tiles, and the first player turn becomes playable.} & \wcell{2.55cm}{Matched on clean rerun. Bootstrap and first-turn readiness both passed.} & \wcell{2.10cm}{\code{GameRootTests}, \code{BattleFlowPlayModeTests}} \\
\wcell{0.95cm}{TC-02} & \wcell{2.20cm}{Turn reset and draw cycle} & \wcell{2.55cm}{Advance from one player turn to the next after card use and discard activity.} & \wcell{2.55cm}{Card-play quota resets and a fresh hand is drawn according to deck state.} & \wcell{2.55cm}{Matched on rerun. Turn-loop and deck lifecycle checks passed.} & \wcell{2.10cm}{\code{TurnManagerTests}, \code{DeckManagerTests}} \\
\wcell{0.95cm}{TC-03} & \wcell{2.20cm}{Move card on a valid target tile} & \wcell{2.55cm}{Select a move card and click a reachable, in-bounds tile.} & \wcell{2.55cm}{The unit moves to the selected tile and occupancy updates correctly.} & \wcell{2.55cm}{Matched on rerun. Resolver and grid assertions both passed.} & \wcell{2.10cm}{\code{CardResolverTests}, \code{GridManagerTests}} \\
\wcell{0.95cm}{TC-04} & \wcell{2.20cm}{Strike / guard interaction} & \wcell{2.55cm}{Apply strike or guard through card resolution and the UI card-selection flow.} & \wcell{2.55cm}{Strike damages an adjacent enemy; guard applies temporary defence and is consumed correctly.} & \wcell{2.55cm}{Matched on rerun. Direct logic and UI-triggered branches passed.} & \wcell{2.10cm}{\code{CardResolverTests}, \code{UnitControllerTests}, \code{BattleUITests}} \\
\wcell{0.95cm}{TC-05} & \wcell{2.20cm}{Invalid target prompt} & \wcell{2.55cm}{Select a card and attempt an invalid tile, wrong range, or friendly target.} & \wcell{2.55cm}{The action is rejected and the UI shows a clear corrective prompt.} & \wcell{2.55cm}{Matched on rerun. Prompt and rejection paths both passed.} & \wcell{2.10cm}{\code{BattleUITests}, \code{CardButtonViewTests}} \\
\wcell{0.95cm}{TC-06} & \wcell{2.20cm}{Enemy AI decision step} & \wcell{2.55cm}{Provide multiple candidate player targets with distance differences and dead/alive combinations.} & \wcell{2.55cm}{AI picks the nearest alive player and then moves or attacks according to state.} & \wcell{2.55cm}{Matched on rerun. Selection and turn orchestration checks passed.} & \wcell{2.10cm}{\code{EnemyAITests}, \code{TurnManagerTests}} \\
\wcell{0.95cm}{TC-07} & \wcell{2.20cm}{Battle end lock and outcome display} & \wcell{2.55cm}{Drive the battle to a terminal win or loss condition.} & \wcell{2.55cm}{The loop locks, no further actions are accepted, and a stable outcome state is exposed.} & \wcell{2.55cm}{Matched on rerun. Regression checks and UI lock behaviour passed.} & \wcell{2.10cm}{\code{TurnManagerTests}, \code{BattleUITests}} \\
\bottomrule
\end{longtable}
\normalsize
\setlength{\tabcolsep}{6pt}

\section{Final Suite Inventory}

\setlength{\tabcolsep}{4pt}
\footnotesize
\begin{longtable}{ll}
\caption{Final suite inventory used by the validation results.}
\label{tab:suite-inventory}\\
\toprule
\wcell{4.20cm}{\textbf{Suite file, mode, and method count}} & \wcell{8.10cm}{\textbf{Main role in the validated suite}} \\
\midrule
\endfirsthead
\toprule
\wcell{4.20cm}{\textbf{Suite file, mode, and method count}} & \wcell{8.10cm}{\textbf{Main role in the validated suite}} \\
\midrule
\endhead
\wcell{4.20cm}{\code{TurnManagerTests}\\EditMode, 3 methods} & \wcell{8.10cm}{Preserve the battle-end regression layer and verify turn-loop correctness.} \\
\wcell{4.20cm}{\code{DeckManagerTests}\\EditMode, 6 methods} & \wcell{8.10cm}{Stabilise hand, deck, discard, and reshuffle rules.} \\
\wcell{4.20cm}{\code{EnemyAITests}\\EditMode, 4 methods} & \wcell{8.10cm}{Separate deterministic AI rules from turn-loop orchestration.} \\
\wcell{4.20cm}{\code{UnitControllerTests}\\EditMode, 6 methods} & \wcell{8.10cm}{Lock state changes around HP, guard, death, and movement.} \\
\wcell{4.20cm}{\code{GridManagerTests}\\EditMode, 7 methods} & \wcell{8.10cm}{Cover the grid as a shared dependency for move, strike, and push logic.} \\
\wcell{4.20cm}{\code{CardResolverTests}\\EditMode, 6 methods} & \wcell{8.10cm}{Test card semantics directly without UI indirection.} \\
\wcell{4.20cm}{\code{BattleUITests}\\EditMode, 19 methods} & \wcell{8.10cm}{Capture UI prompt logic, strengthened onboarding and enemy-phase summaries, auto-resolve behaviour, helper branches, and action-log updates.} \\
\wcell{4.20cm}{\code{GameRootTests}\\EditMode, 2 methods} & \wcell{8.10cm}{Verify scene bootstrap and dependency discovery without a full play session.} \\
\wcell{4.20cm}{\code{TileViewTests}\\EditMode, 3 methods} & \wcell{8.10cm}{Verify tile coordinate, occupancy, and highlight behaviour used by grid/UI flows.} \\
\wcell{4.20cm}{\code{CardButtonViewTests}\\EditMode, 1 method} & \wcell{8.10cm}{Verify the click-binding handoff from button to battle UI.} \\
\wcell{4.20cm}{\code{BattleFlow}\\\code{PlayModeTests}\\PlayMode, 1 method} & \wcell{8.10cm}{Provide one end-to-end smoke checkpoint for battle bootstrap and first playable turn.} \\
\bottomrule
\end{longtable}
\normalsize
\setlength{\tabcolsep}{6pt}

The test plan has therefore closed its original gaps: every targeted runtime class is directly tested, the smoke path is rerun-backed, and the supporting records now describe a validated suite rather than a hypothetical one.
