\appendix

\chapter{Supporting Evidence Index}

\begin{table}[H]
\centering
\small
\begin{tabular}{lll}
\toprule
\wcell{4.7cm}{\textbf{Source file}} & \wcell{2.4cm}{\textbf{Type}} & \wcell{5.1cm}{\textbf{Use in this report}} \\
\midrule
\wcell{4.7cm}{`doc/src/project-records/testing/wr3-test-inventory-2026-04-17.md`} & \wcell{2.4cm}{Testing record} & \wcell{5.1cm}{Source for suite counts, module coverage, and appendix planning} \\
\wcell{4.7cm}{`doc/src/project-records/testing/wr3-execution-summary-2026-04-17.md`} & \wcell{2.4cm}{Testing record} & \wcell{5.1cm}{Source for the final rerun-backed execution summary and suite totals} \\
\wcell{4.7cm}{`doc/src/project-records/testing/wr3-requirements-coverage-matrix-2026-04-17.md`} & \wcell{2.4cm}{Testing record} & \wcell{5.1cm}{Source for Table \ref{tab:requirements-coverage}} \\
\wcell{4.7cm}{`doc/src/project-records/testing/wr3-coverage-export-2026-04-17.md`} & \wcell{2.4cm}{Testing record} & \wcell{5.1cm}{Source for the archived coverage totals, class metrics, and export-path narrative} \\
\wcell{4.7cm}{`doc/src/project-records/testing/wr3-defect-log-2026-04-17.md`} & \wcell{2.4cm}{Testing record} & \wcell{5.1cm}{Source for the defect tables in Chapter 4} \\
\wcell{4.7cm}{`doc/src/project-records/process/wr3-milestone-status-2026-04-17.md`} & \wcell{2.4cm}{Process record} & \wcell{5.1cm}{Source for the final milestone closure table in Chapter 5} \\
\wcell{4.7cm}{`doc/src/project-records/testing/coverage/2026-04-17/Report/`} & \wcell{2.4cm}{Coverage archive} & \wcell{5.1cm}{Contains the HTML coverage report, badges, and summary files cited in Chapter 4} \\
\wcell{4.7cm}{`doc/src/project-records/testing/prototype-accuracy-editmode-run-2026-04-02.md`} & \wcell{2.4cm}{Testing record} & \wcell{5.1cm}{Earlier regression record for the battle-end fix referenced in Chapter 4} \\
\wcell{4.7cm}{`doc/src/project-records/process/wr3-execution-plan-2026-04-17.md`} & \wcell{2.4cm}{Process record} & \wcell{5.1cm}{Canonical WR3 scope, milestones, testing targets, and acceptance gates} \\
\wcell{4.7cm}{`doc/src/project-records/process/wr3-milestones-and-owners-2026-04-17.md`} & \wcell{2.4cm}{Process record} & \wcell{5.1cm}{Source for the milestone, owner, and completion-evidence tables} \\
\wcell{4.7cm}{`doc/src/project-records/process/README.md`} & \wcell{2.4cm}{Process record} & \wcell{5.1cm}{Explains how repo and board evidence packages are organised} \\
\wcell{4.7cm}{`doc/src/wr3-latex/wr3-scoring-summary.md`} & \wcell{2.4cm}{Local sample analysis} & \wcell{5.1cm}{Drives the report's table-heavy structure and evidence emphasis} \\
\bottomrule
\end{tabular}
\caption{Supporting records referenced by the final draft.}
\label{tab:appendix-evidence-index}
\end{table}

\section{Testing and Validation Meeting}

\textbf{Date:} 15/04/2026 \\
\textbf{Format:} Online \\
\textbf{Chair:} Guangjun HU \\
\textbf{Secretary:} Zehan CHEN

\subsection{Attendance}

\begin{itemize}
    \item Guangjun HU -- present
    \item Hongshuo HU -- present
    \item Cheng YE -- present
    \item Zehan CHEN -- present
\end{itemize}

\subsection{Agenda}

\begin{enumerate}
    \item Review WR2 heuristic walkthrough findings and defect triage.
    \item Confirm the test strategy and automated test scope.
    \item Allocate report drafting tasks.
    \item Set deadlines for remaining open bugs and final submission preparation.
\end{enumerate}

\subsection{Progress Since Last Meeting}

Since the WR2 closeout meeting, the team has:

\begin{itemize}
    \item Confirmed the WR2 closeout state on 02/04/2026 before starting the validation work.
    \item Applied the battle-end accuracy fix and verified it with EditMode tests.
    \item Created the initial test log and defect log under \code{doc/src/project-records/testing/}.
\end{itemize}

\subsection{Key Discussion Points}

\begin{itemize}
    \item The high-severity battle-end gap (\code{WR2-BUG-03}) was confirmed fixed by the EditMode smoke test. No additional runtime changes were required for this issue.
    \item Onboarding clarity (\code{WR2-BUG-01}) and enemy-phase emphasis (\code{WR2-BUG-02}) were judged medium severity at triage time, then carried into the final polish pass and closed with rerun-backed evidence before the evidence freeze.
    \item The team agreed to keep the report within the course template structure and not to introduce new gameplay features during the validation cycle.
    \item GitHub pull-request review remains the canonical collaboration path; final submission changes must pass through reviewed and merged pull requests.
\end{itemize}

\subsection{Decisions Made}

\begin{itemize}
    \item Scope is limited to testing documentation, defect tracking, and report assembly.
    \item All four members will contribute to the final report draft, with Cheng YE leading LaTeX compilation and Hongshuo HU leading runtime verification.
    \item The two inherited medium-severity usability issues were accepted into the final polish pass and had to be closed with named rerun evidence before the evidence freeze.
\end{itemize}

\subsection{Action Items}

\begin{table}[H]
\centering
\footnotesize
\setlength{\tabcolsep}{4pt}
\begin{tabular}{llll}
\toprule
\wcell{4.2cm}{\textbf{Task}} & \wcell{2.0cm}{\textbf{Owner}} & \wcell{1.9cm}{\textbf{Due}} & \wcell{2.8cm}{\textbf{Review owner}} \\
\midrule
\wcell{4.2cm}{Draft LaTeX sections and tables} & \wcell{2.0cm}{Cheng YE} & \wcell{1.9cm}{16/04/2026} & \wcell{2.8cm}{Guangjun HU} \\
\wcell{4.2cm}{Run EditMode tests and capture results} & \wcell{2.0cm}{Hongshuo HU} & \wcell{1.9cm}{15/04/2026} & \wcell{2.8cm}{Guangjun HU} \\
\wcell{4.2cm}{Update defect register and meeting minutes} & \wcell{2.0cm}{Zehan CHEN} & \wcell{1.9cm}{16/04/2026} & \wcell{2.8cm}{Cheng YE} \\
\wcell{4.2cm}{Final integration check in Unity editor} & \wcell{2.0cm}{Hongshuo HU} & \wcell{1.9cm}{17/04/2026} & \wcell{2.8cm}{Whole team} \\
\bottomrule
\end{tabular}
\caption{Action items agreed in the testing and validation meeting.}
\label{tab:appendix-meeting-actions}
\end{table}

\subsection{Issue Closure Status}

\begin{itemize}
    \item \code{WR2-BUG-01}: fixed and verified by the final \code{BattleUI} rerun after the prompt and next-step messaging updates.
    \item \code{WR2-BUG-02}: fixed and verified by the final \code{BattleUI} and \code{TurnManager} reruns after the enemy summary emphasis updates.
    \item Automated coverage for \code{GridManager} and \code{CardResolver} was pending at the time of the meeting and was later completed during the final coverage pass.
\end{itemize}

\subsection{Next Meeting}

\begin{itemize}
    \item Tentative date: 24/04/2026.
    \item Main agenda: final submission checklist, closed-bug retest review, and repository submission-readiness confirmation.
\end{itemize}

\chapter{Representative Test Case Inventory}

\small
\begin{longtable}{llll}
\caption{Representative test case inventory for the final suite.}
\label{tab:appendix-test-cases}\\
\toprule
\wcell{2.3cm}{\textbf{Module / suite}} & \wcell{5.4cm}{\textbf{Test case}} & \wcell{2.7cm}{\textbf{Purpose}} & \wcell{1.4cm}{\textbf{Label}} \\
\midrule
\endfirsthead
\toprule
\wcell{2.3cm}{\textbf{Module / suite}} & \wcell{5.4cm}{\textbf{Test case}} & \wcell{2.7cm}{\textbf{Purpose}} & \wcell{1.4cm}{\textbf{Label}} \\
\midrule
\endhead
\wcell{2.3cm}{TurnManager} & \wcell{5.4cm}{\code{StartBattle_WhenNoEnemyUnits_EndsInPlayerVictory}} & \wcell{2.7cm}{Verify immediate victory when the enemy side is empty at battle start.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{TurnManager} & \wcell{5.4cm}{\code{StartBattle_WhenNoPlayerUnits_EndsInEnemyVictory}} & \wcell{2.7cm}{Verify immediate defeat when the player side is empty at battle start.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{TurnManager} & \wcell{5.4cm}{\code{EndPlayerTurn_WhenEnemyDefeatsLastPlayer_DoesNotRestartPlayerTurn}} & \wcell{2.7cm}{Prevent the loop from incorrectly starting a new player turn after defeat.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{DeckManager} & \wcell{5.4cm}{\code{ResetDeck_WithoutStartingDeck_UsesFallbackDeck}} & \wcell{2.7cm}{Confirm the fallback deck is created when no starting deck is configured.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{DeckManager} & \wcell{5.4cm}{\code{DrawForTurn_DrawsConfiguredNumberOfCards}} & \wcell{2.7cm}{Confirm the turn draw count uses the configured cards-per-turn value.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{DeckManager} & \wcell{5.4cm}{\code{DiscardFromHand_MovesCardToDiscardPile}} & \wcell{2.7cm}{Confirm single-card discard behaviour.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{DeckManager} & \wcell{5.4cm}{\code{DiscardHand_MovesAllCardsToDiscardPile}} & \wcell{2.7cm}{Confirm whole-hand discard behaviour at turn reset.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{DeckManager} & \wcell{5.4cm}{\code{Draw_WhenDrawPileEmpty_ReshufflesDiscardPile}} & \wcell{2.7cm}{Confirm discard-to-draw reshuffle behaviour.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{DeckManager} & \wcell{5.4cm}{\code{Draw_WhenNoCardsRemain_LeavesHandUnchanged}} & \wcell{2.7cm}{Confirm the empty-deck branch exits safely.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{EnemyAI} & \wcell{5.4cm}{\code{ManhattanDistance_ReturnsAbsoluteGridDistance}} & \wcell{2.7cm}{Validate the AI distance metric used for targeting.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{EnemyAI} & \wcell{5.4cm}{\code{FindNearestPlayer_SkipsDeadUnitsAndReturnsClosestAliveTarget}} & \wcell{2.7cm}{Confirm the AI ignores dead targets and chooses the nearest alive player.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{EnemyAI} & \wcell{5.4cm}{\code{GetStepToward_PrefersHorizontalStepWhenAxesTie}} & \wcell{2.7cm}{Confirm deterministic tie-breaking in step selection.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{EnemyAI} & \wcell{5.4cm}{\code{GetStepToward_UsesVerticalStepWhenVerticalDeltaIsLarger}} & \wcell{2.7cm}{Confirm vertical movement preference when vertical distance is larger.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{UnitController} & \wcell{5.4cm}{\code{CreateUnit_InitializesCurrentHpFromConfiguredValue}} & \wcell{2.7cm}{Confirm runtime creation respects the configured max HP.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{UnitController} & \wcell{5.4cm}{\code{TakeDamage_ReducesHitPoints}} & \wcell{2.7cm}{Confirm standard damage application.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{UnitController} & \wcell{5.4cm}{\code{Guarding_ReducesNextHitAndThenClearsGuard}} & \wcell{2.7cm}{Confirm one-hit guard consumption behaviour.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{UnitController} & \wcell{5.4cm}{\code{Heal_DoesNotExceedMaxHp}} & \wcell{2.7cm}{Confirm healing clamps at max HP.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{UnitController} & \wcell{5.4cm}{\code{TakeDamage_ToZero_DisablesGameObject}} & \wcell{2.7cm}{Confirm unit death deactivates the object.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{UnitController} & \wcell{5.4cm}{\code{SetGridPosition_UpdatesGridAndWorldPosition}} & \wcell{2.7cm}{Confirm grid/world position synchronisation.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{GridManager} & \wcell{5.4cm}{\code{GenerateGrid_CreatesExpectedTiles}} & \wcell{2.7cm}{Confirm grid size and bounds setup.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{GridManager} & \wcell{5.4cm}{\code{TryPlaceUnit_PlacesUnitAndUpdatesOccupancy}} & \wcell{2.7cm}{Confirm unit placement and occupancy bookkeeping.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{GridManager} & \wcell{5.4cm}{\code{TryMoveUnit_MovesUnitAndClearsPreviousTile}} & \wcell{2.7cm}{Confirm movement updates both origin and destination tiles.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{GridManager} & \wcell{5.4cm}{\code{TryPushUnit_RejectsOutOfBoundsDestination}} & \wcell{2.7cm}{Confirm push logic rejects invalid destinations.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{GridManager} & \wcell{5.4cm}{\code{GetNeighbors_ReturnsOrthogonalInBoundsCoordinates}} & \wcell{2.7cm}{Confirm neighbour enumeration.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{GridManager} & \wcell{5.4cm}{\code{GetTilesInRange_ReturnsBreadthFirstManhattanRange}} & \wcell{2.7cm}{Confirm BFS range expansion used by move/attack highlighting.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{GridManager} & \wcell{5.4cm}{\code{HighlightMoveRange_TracksHighlightedTilesAndClearHighlights_ResetsState}} & \wcell{2.7cm}{Confirm highlight tracking and cleanup.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{CardResolver} & \wcell{5.4cm}{\code{GetValidTiles_Move_ReturnsUnoccupiedTilesWithinRange}} & \wcell{2.7cm}{Confirm move-card targeting excludes occupied tiles.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{CardResolver} & \wcell{5.4cm}{\code{ResolveTileCard_Move_MovesUnitToTargetTile}} & \wcell{2.7cm}{Confirm move-card execution updates the unit and grid.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{CardResolver} & \wcell{5.4cm}{\code{ResolveTileCard_Guard_SetsUnitGuarding}} & \wcell{2.7cm}{Confirm guard-card resolution sets the defensive state.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{CardResolver} & \wcell{5.4cm}{\code{ResolveUnitCard_Strike_DamagesEnemyAndClearsTileWhenTargetDies}} & \wcell{2.7cm}{Confirm strike damage and occupancy cleanup on death.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{CardResolver} & \wcell{5.4cm}{\code{ResolveUnitCard_Push_DamagesAndMovesEnemyBack}} & \wcell{2.7cm}{Confirm push damage plus displacement.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{CardResolver} & \wcell{5.4cm}{\code{ResolveUnitCard_RejectsFriendlyTarget}} & \wcell{2.7cm}{Confirm enemy-only targeting rules.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{BattleUI} & \wcell{5.4cm}{\code{SelectCard_WithoutSelectedUnit_RequestsUnitSelection}} & \wcell{2.7cm}{Confirm the UI prompts for unit selection before card use.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{BattleUI} & \wcell{5.4cm}{\code{SelectCard_GuardCardWithSelectedUnit_AutoResolvesAndConsumesCardPlay}} & \wcell{2.7cm}{Confirm self-target guard cards resolve immediately.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{BattleUI} & \wcell{5.4cm}{\code{TryPlayCardOnTile_InvalidTarget_ReturnsFalseAndKeepsCardSelected}} & \wcell{2.7cm}{Confirm invalid tile targets do not resolve and keep state visible.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{BattleUI} & \wcell{5.4cm}{\code{TryPlayCardOnUnit_ValidStrike_ConsumesPlayAndUpdatesActionLog}} & \wcell{2.7cm}{Confirm valid strike actions update both play count and action log.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{BattleUI} & \wcell{5.4cm}{\code{SelectCard_AfterBattleEnded_ShowsBattleOutcome}} & \wcell{2.7cm}{Confirm UI lock and outcome message after battle end.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{GameRoot} & \wcell{5.4cm}{\code{Awake_FindsDependenciesWhenSerializedFieldsAreEmpty}} & \wcell{2.7cm}{Confirm dependency discovery in the scene bootstrap object.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{GameRoot} & \wcell{5.4cm}{\code{Start_InitializesManagersPlacesUnitsAndStartsBattle}} & \wcell{2.7cm}{Confirm bootstrap wiring from managers to first battle state.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{TileView} & \wcell{5.4cm}{\code{Initialize_SetsCoordinate}} & \wcell{2.7cm}{Confirm tile coordinate initialisation.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{TileView} & \wcell{5.4cm}{\code{SetOccupantAndClearOccupant_UpdateOccupancyState}} & \wcell{2.7cm}{Confirm tile occupancy bookkeeping.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{TileView} & \wcell{5.4cm}{\code{HighlightMethods_CreateRuntimeMaterialAndDoNotThrow}} & \wcell{2.7cm}{Confirm tile visual highlight methods are safe to call at runtime.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{CardButtonView} & \wcell{5.4cm}{\code{Bind_ClickInvokesBattleUiSelection}} & \wcell{2.7cm}{Confirm button binding forwards the selected card to the battle UI.} & \wcell{1.4cm}{Verified} \\
\wcell{2.3cm}{PlayMode smoke} & \wcell{5.4cm}{\code{GameRoot_Start_InitializesBattleReadyState}} & \wcell{2.7cm}{Confirm the scene reaches a playable battle-ready state in PlayMode.} & \wcell{1.4cm}{Verified} \\
\bottomrule
\end{longtable}

\normalsize
