\appendix

\chapter{Meeting Minutes and Working Records}

\section{Recovered Checkpoint (15/03/2026)}

No formal implementation meeting minutes were archived in the local workspace for the first prototype checkpoint. To avoid inventing details, the following recovered checkpoint summary was compiled from dated artifacts that are present in the repository: the architecture constraints note, the first-pass script plan, and the prototype screenshots created on 15/03/2026.

\begin{itemize}
\item \textbf{Record type:} recovered implementation checkpoint compiled from local artifacts rather than formal minutes.
\item \textbf{Date:} 15/03/2026.
\item \textbf{Attendance:} exact attendance was not archived in the local workspace and should be replaced with confirmed team attendance if chat or calendar records are available.
\item \textbf{Sources used:} \path{demo_architecture_constraints.md}, \path{demo_first_pass_scripts.md}, and prototype screenshots timestamped on 15/03/2026.
\item \textbf{Main focus:} reduce the original game concept to one battle scene, four starter cards, a readable control loop, and a minimum set of scripts that can compile and run inside the existing Unity project.
\item \textbf{Confirmed decisions:} single-battle scope, shared unit controller, deterministic enemy response, explicit card types, button-driven card interaction, and no campaign or deckbuilding systems in WR2.
\item \textbf{Follow-up actions:} finish the first gameplay skeleton, refresh UML diagrams to match implementation, and gather prototype evidence for WR2.
\end{itemize}

\section{WR2 Evidence Freeze Note}

The WR2 documentation pack uses an evidence freeze line of \textbf{02/04/2026 12:00}. This freeze is recorded in \path{wr2-snapshot-freeze-2026-04-02.md}. After that point, only changes that materially improve submission quality should be described in WR2. New features developed later should be documented in WR3 or the final report instead of being backfilled into this report.

\section{Supporting Record Index}

The local record structure created during WR2 is summarised below and stored under \texttt{doc/src/project-records}.

\begin{itemize}
\item \path{wr2-asset-register.md}: reusable evidence list, missing items, suggested owners, and due times.
\item \path{process/canonical-repo-evidence-2026-04-02.md}: canonical repository evidence note, historical discovery summary, and the current recommendation for using merged GitHub history as repo-workflow evidence.
\item \path{process/task-board-evidence-2026-04-02.md}: task-board evidence note, discovery summary, and import checklist.
\item \path{process/discovery/README.md}: command-level discovery artifacts explaining what was checked from this workspace.
\item \path{meetings/meeting-minutes-template.md}: lightweight meeting template for future weekly records.
\item \path{meetings/implementation-checkpoint-recovered-2026-03-15.md}: transparent recovered note based on local artifacts.
\item \path{decisions/wr2-implementation-decisions.md}: decision log extracted from the current implementation direction.
\item \path{collaboration-history-2026-04-02.md}: concise explanation of the move from early WeChat/Overleaf coordination to the current GitHub PR workflow.
\item \path{validation/wr2-heuristic-walkthrough-2026-04-01.md}: internal WR2 walkthrough and findings.
\item \path{testing/prototype-accuracy-editmode-run-2026-04-02.md}: EditMode verification note for the battle-end accuracy fix.
\item \path{testing/wr3-prep-log-2026-04-01.md}: initial test and bug tracking preparation note for the next report cycle.
\end{itemize}

These records are intentionally lightweight. Their purpose is to stop evidence loss between WR2 and WR3, not to pretend that the record-keeping process was already complete earlier in the prototype cycle.
