\section{Meeting Record Scope}

This appendix section contains the meeting records currently preserved inside the workspace. Where a record was reconstructed from dated artifacts rather than preserved as a complete formal minute set, it remains labelled as \textit{recovered}. This distinction should be preserved in the final report rather than hidden.

\section{Recovered Implementation Checkpoint}

\textbf{Date:} 15/03/2026 \\
\textbf{Type:} recovered checkpoint note \\
\textbf{Attendance:} exact attendance not archived in this workspace

\subsection{Purpose}

Turn the WR1 proposal into a minimum playable prototype that could demonstrate:

\begin{itemize}
    \item a tactical grid;
    \item card-driven actions;
    \item a visible turn loop;
    \item enemy response.
\end{itemize}

\subsection{Recovered Decisions}

\begin{itemize}
    \item Use one battle scene only for the early playable version.
    \item Keep the board at 6x6 for the first prototype.
    \item Limit the starter prototype to four cards: Move, Strike, Guard, and Push.
    \item Use one shared `UnitController` for player and enemy units.
    \item Keep enemy behaviour deterministic and minimal.
    \item Prefer simple button-driven card selection over drag-and-drop interaction.
\end{itemize}

\subsection{Recovered Follow-up Tasks}

\begin{itemize}
    \item Implement the first-pass script list and get the scene running.
    \item Refresh the architecture diagrams so they match the actual scripts.
    \item Capture prototype screenshots for WR2.
    \item Start recording validation and testing notes separately from design notes.
\end{itemize}

\section{WR1 Kickoff Meeting}

\textbf{Date:} 17/03/2026 \\
\textbf{Attendance:} Guangjun HU, Hongshuo HU, Zehan CHEN

\subsection{Context}

This meeting was used to share initial game ideas, narrow the coursework direction, and assign the first WR1 tasks.

\subsection{Decisions}

\begin{itemize}
    \item Confirm \projectname{} as the project direction.
    \item Agree the initial role allocation.
    \item Set the first delivery expectations for WR1 materials.
\end{itemize}

\subsection{Follow-up}

\begin{itemize}
    \item Prepare initial WR1 materials between 18/03/2026 and 19/03/2026.
    \item Carry the outcome into WR1 project direction, division of labour, and requirements sections.
\end{itemize}

\section{WR1 Alignment Meeting}

\textbf{Date:} 18/03/2026 \\
\textbf{Attendance:} Guangjun HU, Cheng YE

\subsection{Context}

This meeting aligned the current requirement scope around a tactical card battle demo, assigned UML-related work, and standardised a lightweight minute-taking format.

\subsection{Decisions}

\begin{itemize}
    \item Confirm the WR1 scope around a tactical card battle demo.
    \item Assign UML diagram production.
    \item Define a unified meeting-minutes format for later weeks.
\end{itemize}

\subsection{Follow-up}

\begin{itemize}
    \item Finalise WR1 alignment by 19/03/2026.
    \item Reuse the agreed meeting-minutes format in later weekly cycles.
\end{itemize}

\section{Testing and Validation Meeting}

\textbf{Date:} 15/04/2026 \\
\textbf{Format:} Online \\
\textbf{Chair:} Guangjun HU \\
\textbf{Secretary:} Zehan CHEN

\subsection{Attendance}

\begin{itemize}
    \item Guangjun HU -- present
    \item Hongshuo HU -- present
    \item Cheng YE -- present
    \item Zehan CHEN -- present
\end{itemize}

\subsection{Agenda}

\begin{enumerate}
    \item Review WR2 heuristic walkthrough findings and defect triage.
    \item Confirm the test strategy and automated test scope.
    \item Allocate report drafting tasks.
    \item Set deadlines for remaining open bugs and final submission preparation.
\end{enumerate}

\subsection{Progress Since Last Meeting}

\begin{itemize}
    \item Confirm the WR2 closeout state on 02/04/2026 before starting the validation work.
    \item Apply the battle-end accuracy fix and verify it with EditMode tests.
    \item Create the initial test log and defect log under \code{doc/src/project-records/testing/}.
\end{itemize}

\subsection{Key Discussion Points}

\begin{itemize}
    \item The high-severity battle-end gap was confirmed fixed by the EditMode smoke test.
    \item Onboarding clarity and enemy-phase emphasis were carried into the final polish pass and had to be closed with rerun-backed evidence before the evidence freeze.
    \item The team agreed to keep the report within the course template structure and not to introduce unrelated gameplay work during the validation cycle.
    \item GitHub pull-request review remained the canonical collaboration path for submission-facing changes.
\end{itemize}

\subsection{Decisions Made}

\begin{itemize}
    \item Scope was limited to testing documentation, defect tracking, and report assembly for this cycle.
    \item All four members would contribute to the final report draft.
    \item The inherited usability issues had to be closed with named rerun evidence before the evidence freeze.
\end{itemize}

\subsection{Action Items}

\begin{table}[H]
\centering
\footnotesize
\setlength{\tabcolsep}{4pt}
\begin{tabular}{llll}
\toprule
\wcell{4.1cm}{\textbf{Task}} & \wcell{2.0cm}{\textbf{Owner}} & \wcell{1.8cm}{\textbf{Due}} & \wcell{2.8cm}{\textbf{Review owner}} \\
\midrule
\wcell{4.1cm}{Draft LaTeX sections and tables} & \wcell{2.0cm}{Cheng YE} & \wcell{1.8cm}{16/04/2026} & \wcell{2.8cm}{Guangjun HU} \\
\wcell{4.1cm}{Run EditMode tests and capture results} & \wcell{2.0cm}{Hongshuo HU} & \wcell{1.8cm}{15/04/2026} & \wcell{2.8cm}{Guangjun HU} \\
\wcell{4.1cm}{Update defect register and meeting minutes} & \wcell{2.0cm}{Zehan CHEN} & \wcell{1.8cm}{16/04/2026} & \wcell{2.8cm}{Cheng YE} \\
\wcell{4.1cm}{Final integration check in Unity editor} & \wcell{2.0cm}{Hongshuo HU} & \wcell{1.8cm}{17/04/2026} & \wcell{2.8cm}{Whole team} \\
\bottomrule
\end{tabular}
\caption{Action items agreed in the testing and validation meeting.}
\label{tab:final-meeting-actions}
\end{table}

\subsection{Issue Closure Status}

\begin{itemize}
    \item Onboarding clarity was later closed through the post-WR3 HUD and title-flow improvements.
    \item Enemy-phase emphasis was later closed through UI and prompt updates.
    \item Coverage completion remained pending at the time of the meeting and was finished later in the cycle.
\end{itemize}

\subsection{Next Meeting}

\begin{itemize}
    \item Tentative date: 24/04/2026.
    \item Main agenda: final submission checklist, closed-bug retest review, and repository submission-readiness confirmation.
\end{itemize}

\section{Current Gap Note}

This workspace does not yet contain a stronger formally archived record for any later final sign-off meeting. If another confirmed formal meeting record exists outside the workspace, it should still be imported before submission.
